\specialhead{ACKNOWLEDGMENT}

% http://matt.might.net/articles/phd-school-in-pictures/
Over the past seven years, I have devoted nearly all of my time and energy into learning the skills and
  developing the systems that have allowed me to make this contribution.
I would've been unable to achieve this feat without the support and guidance of others.

First and foremost, I must thank my partner: Dana Cardona.
Her love, support, and feedback has motivated and sustained me during my time as a graduate student.
In our five years together I have found more stability and purpose than I thought was possible.

I am grateful to my parents for their ongoing encouragement and for fostering my curiosity.
Thank you for all that you have done and continue to do.

Also, to my friend Lucas Cotterell:
it was in a conversation with Luc that I decided that I could and would pursue a doctorate degree.
His long-lasting friendship has helped me achieve this goal.

Next, I thank my labmates Peter Honig, Zach Jablons, Jason Parham, and Hendrik Weideman.
Our discussions have been invaluable and are responsible for a significant portion of my understanding of
  computer vision, machine learning, and neural networks.

I graciously thank my advisor --- Chuck Stewart --- whose guidance helped me navigate my research, grow
  professionally and personally, and whose writing style has caused me to develop a fondness for em dashes.

To my committee members:
Barb Cutler, Rich Rake, and Bülent Yener, whose suggestions, comments, and challenges successfully pushed me from
  my candidacy to the completion of my dissertation.
I am thankful to them and to the other RPI professors who have taken the time to share their insight and discuss
  research problems with me.

I am immensely grateful to Bill and Naomi Hoffman for all they have done to open this path for me.
I am filled with appreciation for them and the many others at Kitware who acted as teachers and mentors to me.
