\begin{comment}
    ./texfix.py --fixcap --dryrun
    ./texfix.py --findcite --unused-important
    ./texfix.py --findcite --close-keys
    ./texfix.py --fpaths chapter2-related-work.tex --outline --asmarkdown --numlines=999 -w
\end{comment}

% +--- CHAPTER --- 
\chapter{Related work}\label{chap:relatedwork}

    %Individual animal identification is an emerging topic that stems
    %  from the success of algorithms developed in the maturing field of
    %  computer vision.
    %Computer vision algorithms have been applied to the problem of
    %  individual identification for man species such as %
    %skinks, geckos, and
    %  salamanders~\cite{duyck_sloop_2015,martinez_trinidad_relevance_2014}, %
    %mantra rays~\cite{town_manta_2013}, %
    %leatherback sea turtles~\cite{de_zeeuw_computer_2010}, %
    %wildebeests~\cite{bolger_wildid_2011,bolger_computerassisted_2012}, %
    %plains zebras~\cite{lahiri_biometric_2011}, %
    %gorillas and chimpanzees~\cite{loos_automated_2013}, %
    %whale sharks~\cite{holmberg_estimating_2009}, %
    %and African penguins~\cite{loos_automated_2013}.
    %Computer vision algorithms make up the core of the best performing
    %  animal identification techniques.
    %Therefore, the focus of this chapter is to review the computer
    %  vision algorithms themselves.

    To address the individual animal identification problem we draw
      upon related research in
    %---
    feature detection~\cite{mikolajczyk_comparison_2005,tuytelaars_local_2007,
      perdoch_efficient_2009},
    %---
    feature description~\cite{lowe_distinctive_2004,
      mikolajczyk_performance_2005,simonyan_learning_2014,
      winder_picking_2009,zagoruyko_learning_2015,han_matchnet_2015},
    %---
    approximate nearest neighbor search~\cite{silpa_anan_optimised_2008,
      muja_fast_2009},
    %---
    instance recognition~\cite{sivic_efficient_2009,nister_scalable_2006,
      philbin_object_2007,jegou_hamming_2008,bo_efficient_2009,
      jegou_aggregating_2012, tolias_aggregate_2013},
    %---
    face verification~\cite{chopra_learning_2005,huang_labeled_2007,berg_tom_vs_pete_2012,
      chen_blessing_2013,taigman_deepface_2014}
    %---
    fine-grained recognition~\cite{parkhi_cats_2012,berg_poof_2013,
      gavves_local_2014},
    %---
    category recognition~\cite{lazebnik_beyond_2006,zhang_local_2006,
      mccann_local_2012,boiman_defense_2008,sanchez_compressed_2013},
    %---
    and convolutional neural networks~\cite{krizhevsky_imagenet_2012,
      razavian_cnn_2014, zagoruyko_learning_2015,han_matchnet_2015,arandjelovic_netvlad_2016}.
    %---

    At a high level main questions addressed by the aforementioned
      research can be summarized as:
    How should image features be detected?
    How should detected image features be represented?
    How much invariance should features have?
    Should image features be quantized?
    How should image feature be matched?
    How should feature matches be aggregated?
    How should feature matches be scored?
    How should all of this be done accurately?
    How should all of this be done efficiently?
    Answers to these questions address many of the challenges to animal
      identification previously introduced in~\cref{sec:challenges}.
    %Any solution to animal identification must also address all of these
    %  questions.

    This chapter summarizes literature relevant to addressing these questions
      in the context of animal identification.
    %In this chapter we will describe several other works and their similarities
    %  and differences with animal identification.
    The outline of this chapter is as follows:
    \Cref{sec:featuredetect} will discuss feature detection.
    \Cref{sec:featuredescribe} will discuss feature description.
    \Cref{sec:ann} will discuss approximate nearest neighbor algorithms.
    \Cref{sec:ir,sec:cr,sec:fgr}, will discuss approaches to recognition.
    \Cref{sec:dcnn} will discuss convolutional neural networks.
    %\Cref{sec:otherid} will discuss other works in individual animal
    %  identification.


\input{sec-2-1-featdetect.tex}
\input{sec-2-2-featdescrip.tex}
\input{sec-2-3-neighbors.tex}
\input{sec-2-4-ir.tex}
\input{sec-2-5-cr.tex}
\input{sec-2-6-fgr.tex}
\input{sec-2-7-dcnn.tex}
% L___ CHAPTER ___


%\section{Other animal identification projects}\label{sec:otherid}
        
    \begin{comment}
    %The body of literature related to image-based individual animal
    %  identification is relatively small compared to the other topics
    %  reviewed in this chapter.

    Stripe spotter is an individual identification algorithm developed
      specifically for zebras~\cite{lahiri_biometric_2011}.
    Images are carefully cropped to the flank of animal and the strip
      pattern is discretized using a two dimensional grid called a
      StripeCode.
    The edit distance between pairs of StripeCodes is used to define
      similarity between two individuals.
    This algorithm is only able to achieve a median rank of $4$ for
      datasets with fewer than $85$ individuals and has largely been
      superseded feature matching approaches.

    The most successful animal identification systems have been SIFT
      based.
    SIFT based techniques have been shown to be a reliable way of
      matching many species such as 


    %TODO Need to rewrite this conclusion discussion into related work.

    %Using SIFT~\cite{lowe_distinctive_2004} based techniques we have
    %  been able to outperform previous identification algorithms for
    %  zebras such as Stripe Spotter~\cite{lahiri_biometric_2011}.
    %Our system has been designed to be applicable to many different
    %  species and is more general than other SIFT based systems used to
    %  identify species such as manta rays~\cite{town_manta_2013},
    %  whale sharks~\cite{lahiri_biometric_2011},
    %  leatherback sea turtles~\cite{de_zeeuw_computer_2010}, 
    %  wildebeests~\cite{bolger_wildid_2011,bolger_computerassisted_2012}
    %  salamanders~\cite{duyck_sloop_2015,martinez_trinidad_relevance_2014}.

    Wildbook ECOCEAN \cite{holmberg_estimating_2009}
    constellation matching.

    Gorilla and chimp face identification
      system~\cite{loos_automated_2013}.
    Contains an algorithm system pipeline that detects, aligns, and recognizes
      faces.
    Uses global Gabor features and local SURF features at facial
      fiducial points.
    Facial points are used to align the image into a canonical
      position.
    Concatenates local and global features into a fixed length vector
      and uses SVMS for classification of the faces.
    %Locality Preserving Projections (LPP)

      Penguins~\cite{sherley_spotting_2010}
      shape contexts

    Of the other animal identification projects SLOOP is the most
      similar to ours in terms of design goals --- such as the separation
      of computer vision components from the system
      architecture~\cite{duyck_sloop_2015,martinez_trinidad_relevance_2014}.
    Like our system, SLOOP is able to integrate new computer vision
      algorithms to aid in the task of individual identification.
    However, the algorithms implemented in SLOOP are biased towards
      identifying small deformable amphibian species such as skinks and
      salamanders, similar to the way that our algorithms are biased
      towards large textured mammals such as zebras and giraffes (however
      both systems are designed with many species in mind).
    Both systems require more computer vision tools to address the
      challenges presented in identifying any particular species, and as
      such both systems have been set up to incorporate new computer
      vision algorithms as quickly and cleanly as possible.
    Recent development of SLOOP is targeted towards relevance feedback
      for improving results while we are focused on verification and
      error correction.
    To the best of our knowledge there are no other general purpose
      systems for individual animal identification in development.
    Due to the success of both systems, future collaboration may be in
      order.

    \subsection{Discussion of related techniques}
    \end{comment}
