%! TEX root = main.tex
%\documentclass[chap]{thesis}
\documentclass{thesis}

\input{CrallPramb}
\input{CrallDef}

%\addbibresource{final-bib.bib}
%\defbibheading{secbib}[\bibname]{%
%  \section*{#1}%
%  \markboth{#1}{#1}}

\begin{comment}

https://www.cs.rpi.edu/academics/grad/phd.html
http://gradoffice.rpi.edu/update.do
http://www.rpi.edu/dept/grad/docs/Dissertation%20Checklist.pdf
http://www.rpi.edu/dept/grad/docs/Thesis%20Manual.pdf

http://www.ewp.rpi.edu/hartford/~ernesto/Ancillary-Codes/RPI_Thesis_Templates/Word/manual.pdf

Submit here: http://www.etdadmin.com/cgi-bin/school?siteId=489

    rsync -arvhzP --include='figures*/***' --exclude='*' joncrall@hyrule.cs.rpi.edu:latex/crall-thesis-2017/ ~/latex/crall-thesis-2017
    rsync -arvhzP --include='figures*/***' --exclude='*' joncrall@lev.cs.rpi.edu:latex/crall-thesis-2017/ ~/latex/crall-thesis-2017

    rsync -arvhzP joncrall@hyrule.cs.rpi.edu:latex/crall-thesis-2017/figures5/PZ_Master1/dbstats.tex ~/latex/crall-thesis-2017/figures5/PZ_Master1/dbstats.tex

    rsync -arvhzP --include='figures*/***' --exclude='*' ~/latex/crall-thesis-2017 joncrall@hyrule.cs.rpi.edu:latex/crall-thesis-2017/ 

    rsync -arvhzP ~/latex/crall-thesis-2017/figures2/ joncrall@hyrule.cs.rpi.edu:latex/crall-thesis-2017/figures2
    rsync -arvhzP ~/latex/crall-thesis-2017/figures1/ joncrall@hyrule.cs.rpi.edu:latex/crall-thesis-2017/figures1

    ./texfix.py --fpaths main.tex --outline --asmarkdown --numlines=999 -w --ignoreinputstartswith=def,Crall,header,colordef,figdef
    ./texfix.py --fpaths main.tex --outline --numlines=0 -w --ignoreinputstartswith=def,Crall,header,colordef,figdef
    ./texfix.py --fpaths main.tex --outline --numlines=0 --ignoreinputstartswith=def,Crall,header,colordef,figdef
\end{comment}

\author{Jonathan P. Crall}

\thesistitle{Identifying Individual Animals using Ranking, Verification, and Connectivity}        

\degree{Doctor of Philosophy}        
\department{Computer Science} 
     
\signaturelines{4}     %max number of signature lines is 7        
\thadviser{Dr.\ Charles Stewart}
\memberone{Dr.\ Barbara Cutler}        
\membertwo{Dr.\ Bülent Yener}        
\memberthree{Dr.\ Richard Radke}

\submitdate{June 2017\\(For Graduation August 2017)}        
%\submitdate{June 2016}
%\copyrightyear{2017}   % if omitted, current year is used.        


\begin{document}

\titlepage{}

%\copyrightpage{}         % optional           
\tableofcontents{}        

\listoftables{}          % required if there are tables
\listoffigures{}         % required if there are figures

\specialhead{ACKNOWLEDGMENT}

% http://matt.might.net/articles/phd-school-in-pictures/
Over the past seven years, I have devoted nearly all of my time and energy into learning the skills and
  developing the systems that have allowed me to make this contribution.
I would've been unable to achieve this feat without the support and guidance of others.

First and foremost, I must thank my partner: Dana Cardona.
Her love, support, and feedback has motivated and sustained me during my time as a graduate student.
In our five years together I have found more stability and purpose than I thought was possible.

I am grateful to my parents for their ongoing encouragement and for fostering my curiosity.
Thank you for all that you have done and continue to do.

Also, to my friend Lucas Cotterell:
it was in a conversation with Luc that I decided that I could and would pursue a doctorate degree.
His long-lasting friendship has helped me achieve this goal.

Next, I thank my labmates Peter Honig, Zach Jablons, Jason Parham, and Hendrik Weideman.
Our discussions have been invaluable and are responsible for a significant portion of my understanding of
  computer vision, machine learning, and neural networks.

I graciously thank my advisor --- Chuck Stewart --- whose guidance helped me navigate my research, grow
  professionally and personally, and whose writing style has caused me to develop a fondness for em dashes.

To my committee members:
Barb Cutler, Rich Rake, and Bülent Yener, whose suggestions, comments, and challenges successfully pushed me from
  my candidacy to the completion of my dissertation.
I am thankful to them and to the other RPI professors who have taken the time to share their insight and discuss
  research problems with me.

I am immensely grateful to Bill and Naomi Hoffman for all they have done to open this path for me.
I am filled with appreciation for them and the many others at Kitware who acted as teachers and mentors to me.


\specialhead{ABSTRACT}

In this thesis we address the problem of identifying individual animals using images in the context of assisting
  an ecologist in performing a population census.
We are motivated by events like the ``Great Zebra Count'' where thousands of images of zebras and giraffes were
  collected in Nairobi National Park over two days.
By grouping all images that contain the same individual we can census these populations.
This problem is challenging because images are collected outdoors and contain occlusion, lighting, and quality
  variations and because the animals exhibit viewpoint and pose variations.

Our first contribution is an algorithm that ranks a database of images by their similarity to a query.
A manual reviewer inspects only the top few results for each query --- significantly reducing the search space
  --- and determines if the animals match.
Using this algorithm alone, we analyzed the images from the Great Zebra Count and performed a population census.
Our second contribution is a verification algorithm that determines the probability that two images are from the
  same animal, that they are not, or that there is not enough to decide.
This algorithm is used with the ranking algorithm to re-rank results and automatically verify high confidence
  image pairs.

Our third contribution is a semi-automatic graph identification algorithm.
The approach represents each image as a node in the graph and incrementally forms edges between nodes determined
  to the same animal.
The ranking and verification algorithms are used to search for candidate edges and estimate their probability of
  matching.
Based on these probabilities, edges are prioritized for review and placed in the graph when they are
  automatically verified or manually reviewed.
Redundant connections are added to detect and recover from errors.
A termination criterion determines when identification is finished.
Using the graph algorithm we perform a population census on the scale of the Great Zebra Count using less than
  $25\%$ of the manual reviews required by the original method.

\input{def}

\input{figdef1}
\input{figdef2}
\input{figdef3}
\input{figdef4}
\input{figdef5}

\include{chapter1-intro}
\include{chapter2-related-work}
\include{chapter3-matching}
\include{chapter4-pairclf}
\include{chapter5-graphid}
\include{chapter6-conclusion}

\cleardoublepage
\phantomsection
\addcontentsline{toc}{chapter}{BIBLIOGRAPHY}

\bibliographystyle{ieee}
\bibliography{final-bib}

%\printbibliography


\include{appendix}

\end{document}
% chktex-file 17
