
\section{Why not a fixed length representation?}

Our experiments show that our method outperforms the VLAD-based SMK algorithm.

We use a VLAD representation due to its robustness to pose and viewpoint
  variations that are common in the problem of animal identification.
Even within an annotation animal features may not always be located in the
  same regions.
Methods that extract feature where feature dimensions correspond to spatial
  locations (\ie{} pyramid, grid, or convolutional networks) can be greatly
  impacted by the alignment of the annotation~\cite{wu_viewpoint_2015}.
Because of these disadvantages and the fact that local patterns on the animals
  we identify tend to be distinguishing, we have chosen to primarily focus on
  orderless representations.

*REPORT SMK RESULTS*

\section{Learning the match probability}

This section describes how we learn the annotation-vs-annotation pairwise
  match probability.
This problem is similar to the problem of verification.
However, there are two main differences.
First, we extend our output space to include the case where two annotations
  are not comparable.
Second, is that our annotation representation is an orderless bag of features.
Normally in verification problems (like human re-identification) a fixed
  length vector representation would be computed for each annotation and a
  distance metric would be learned to minimize within-class distance while
  maximizing between-class distance.
However, we provide evidence that our orderless set representation provides a
  richer (albeit more computationally expensive) representation than
  state-of-the-art fixed length representations.
Therefore the second distinction of our problem is that we learn a classifier
  on top a pairwise feature constructed from a set of matches between two
  orderless bag-of-descriptor annotation representations.
This classifier is our match probability mechanism.

The match probability mechanism is a classifier where the inputs are two
  annotations and the output is a probability over the event space:
match, not match, and not comparable.
To build such a classifier the following things are required:
a classification algorithm, a sufficiently large labeled dataset of annotation
  pairs, and a method for extracting features from the dataset.
Furthermore the dataset will need to be split into a testing, training
  dataset, and the training dataset may need to be split into several
  sub-testing sets and validation sets in order to prevent overfitting.


\paragraph{Constructing the annotation pairs}
Given a database of annotations with name labels we first construct a dataset
  of annotation pairs.
There are three types of pairs that we create:
top correct pairs, top incorrect pairs, and random incorrect pairs.
For each annotation in the dataset up to $4$ correct pairs are chosen as the
  top ranked results of a one-vs-many query.
We also choose up to $3$ incorrect results from the top of this list.
These top incorrect pairs are our initial guesses at hard negatives, which
  have been shown to be important for the performance of object categorization
  and person re-identification algorithms~\cite{shi_embedding_2016,
  felzenszwalb_object_2010}.
In addition to the hard-negatives we choose $2$ additional random incorrect
  annotations that serve as easy negatives and expose the classifier to data not
  returned by the one-vs-many algorithm.

After all pairs are generated we remove duplicates and label each pair with a
  multi-class groundtruth label.
For each pair the label is either match, not match, or not comparable.
In our most recent data collection efforts we have asked users to explicitly
  mark the not-comparable and photobomb cases.
In the case that an explicit label is not available for a pair we mark it as
  not comparable if the viewpoints too dissimilar (more than two steps apart),
  otherwise we treat the pair as a match if the two names as not match if the
  names are different.

We (will) experiment with augmenting the three-label state with the photobomb
  label.
In this case the photobomb label is used where it is available, but otherwise
  we do not attempt to infer it.


\paragraph{Constructing the pairwise feature vectors}

Given this set of annotations pairs and labels we construct the features that
  can be fed to the classification algorithm.

We have performed initial experiments using a Siamese network for both feature
  extraction and classification, but the results were poor.
This is likely due to the lack of alignment.
Having accurate alignment has been shown to be critical for pairwise
  verification algorithms such as Deep Face~\cite{taigman_deepface_2014}.
Variations in pose and viewpoint make it challenging to accurately align two
  animals.

We construct our feature vectors based on the results of one-vs-one matching.
This prevents our features from depending heavily on the size of the database.
However, we (will) utilize the database normalizers in order to enrich the
  one-vs-one matching with information about the database-wide distinctivness of
  particular patterns.
We experiment with and without this feature to show the difference.


Given two annotations, one-vs-one matching assigns each feature in the first
  annotation to its reciprocal nearest neighbor in the second annotation.
The second nearest neighbor in the second image is used as an inter-pair
  distinctiveness normalizer.
A score is assigned to each correspondence based on the ratio of the
  normalizer distance to the match distance.
If available, we also compute the \LNBNN{} score of each correspondence based
  on the database normalizer.
Spatial verification is used to remove spatially inconsistent matches.

To construct a fixed length vector we use the top $N=10$ features \wrt{}
  either the ratio or \LNBNN{} score.
Local measures between these features are added to the feature vector.
The local measures we use are:
ratio score, \LNBNN{} score, sift distance, inter-pair normalizer distance,
  database normalizer distance, and spatial verification error (in xy, scale,
  and orientation).
We also add global measures such as GPS, quality, viewpoint, and time.
We both add the individual values of these features as well as deltas between
  them.
For GPS we use the haversine distance, for viewpoint we use radial difference,
  and for all other measures we use the absolute difference.
We also incorporate an extra speed dimension by dividing the GPS delta by the
  time delta.

In the case where a particular data point is missing (\ie{} quality was not
  labeled or there were less than $N$ matches between two annotations), then a
  NaN value is used to indicate missing data.
The problem of learning and predicting with missing data will be addressed by
  the classification algorithm.


\paragraph{Training a classifier}
 
We opt to use a random forest
  classifier~\cite{ho_random_1995,amit_shape_1997,breiman_random_2001} as our
  classification algorithm because
(1) it is an accurate algorithm that can learn complicated decision
  boundaries.
% http://scikit-learn.org/stable/auto_examples/classification/plot_classifier_comparison.html
(2) it is robust to overfitting,
(3) it is fast to train and predict,
(4) it supports a built-in estimate of feature importance,
(4) it is trivially supports probabilistic multi-class classification, and
(5) robust method exist for handling missing
  data~\cite{ding_investigation_2010}.

A random forest is an ensemble of decision trees.
We use the implementation available in
  Scikit-Learn~\cite{pedregosa_scikit-learn_2011}.
Each decision tree is bootstrapped --- \ie{} trained on a randomly selected
  subset of the data.
To grow a decision tree a node chooses a feature dimension and a test that
  induces a binary split of the data.
The chosen feature dimension and tests are chosen to maximize the information
  gain --- \ie{} difference in the entropy (\wrt{} the target labels) in the
  parent and the weighted average of the entropy in the children nodes.
To increase speed and randomness only a fraction ($\sqrt(N_{feats})$) of the
  feature dimensions are considered at each node.
Feature importance is determined by summing the information gain achieved at
  each node split using that feature.
Each tree is grown until there are at most $5$ samples in a leaf.

To handle missing data each decision tree uses the ``separate class''
  method~\cite{ding_investigation_2010}.
The separate class method treats missing values as a separate measurement.
In the case of a categorical feature (like quality or viewpoint) each missing
  value is replaced with an unused value that indicates a new category.
In the case numerical data each NaN value is replaced with an extremely high
  or low value to simulate this effect.
There is strong in the literature that best way to handle missing data is the
  separate class method when the likelihood that data is missing is dependant on
  the target class.
This is the case with many of our features (\eg{} if there are only $N-1$
  correspondences then the last correspondence value will be NaN which is
  indicative of a non match case).
In the case where a NaN value might not be informative (\eg{} quality review
  is missing), then the forest should disregard it just as if it was a normal
  non-predictive feature.

To tune the hyperparameters of the classifier for each species we use grid
  search with $3$-fold cross validation.
Once trained we this classifier to predict the match probabilities $\Pr{M |
  \vec{x}}$ of new annotation pairs.

We evaluate this classifier with the same measures used to evaluate the
  one-vs-many identification algorithm:
the cumulative match characteristic at rank 1 and the receiver operating
  characteristics AUC{}.
This provides a measure of classification accuracy and separability.

\section{Putting Humans in the Loop}

To put human reviewers into the loop we take advantage of a graph algorithm to
(1) choose new pairs to review,
(1) minimize the number of reviews necessary, and
(2) handle split/merge error cases.

We present two new review methods, the first has no automatic decisions and
  the second allows the algorithm to make some automatic decisions.
Both methods improve upon the baseline, which we will present first.

Previously we have used two review methods.
The first method used was to issue a one-vs-many query a single annotation at
  a time and ask the user to review some number of the top results.
Once the user had finished all reviews the next query was issued and the
  process repeated.
This method was slow and cumbersome because of the delay between reviews due
  to computing queries and that often no matching result was found.

The next iteration of the review procedure was to perform all one-vs-many
  queries in batch.
Then the top results of all queries were grouped together, sorted by score and
  presented to the user one at a time.
This was much more satisfying for the user because the correct results all
  jumped to the top of the list.
The user then verified these results and as the matches started becoming more
  and more tenuous further down the list the user could opt to stop and re-run
  the query to search for new matches that could be inferred using the new label
  information.

While this method was an improvement it still had problems.
Consider the matches as a graph where the edges represent information between
  nodes such as the reviewed state.
Many redundant matches were shown.
In principle if you are a perfect reviewer to cluster a group of $N$
  comparable annotations you should only need to make $N-1$ reviews (\ie{} form
  a spanning tree to define a connected component of positive edges).
Furthermore, if a negative review is made between two components, then any
  other edge between those two components is unnecessary to review.

\paragraph{Full Review Algorithm}
We formalize this in our first graph based review algorithm.
Given a graph each edge contains the following information:
\begin{enumerate}
    \item reviewed state:
    this indicates if a user reviewed the edge as match, not match, or not
      comparable.
    Connected components of matching edges denote the current clustering of the graph.

    \item inferred state:
    this indicates if two annotations are the same or different.
    Edges within a connected component are inferred to be the same.
    Edges that do not match are inferred to be different along with all other
      edges between the two components that the not match edge is between.

    \item error state:
    If a not match edge is between two nodes that belong to the same, the
      component is inconsistent and all edges in the component are labeled as
      having an error.
\end{enumerate}
Edges reviewed as not comparable have no influence on the components or error
  state other than denoting that that review has been completed.

The minimum number of reviews needed to achieve the groundtruth labeling for a
  perfect reviewer is $(\sum_{C \in \set{C}} (\card{C} - 1)) +
  \frac{\card{\set{C}}^2 - \card{\set{C}}}{2}$.
Where $\set{C}$ is true set of all components.
This is achieved by reviewing enough positive edges to form a spanning tree
  for each cluster and then reviewing exactly one comparable edge between each
  component.

In this scenario to achieve the minimum number of reviews we sort the edges by
  probability of matching and present them to the user.
As the user makes reviews the state of the graph is dynamically updated and
  any edges that have been inferred are removed from needing review unless they
  are marked as being part of an error case (although in the pure form of this
  framework it is impossible to generate an error state, any true errors will
  just continue to propagate).
We sort by score because we want to review all positive edges first.
If we review negative edges before positive edges there is a change that we
  may review more than one edge between two true components, which is more work
  than is necessary.
In practice we do not review all negative edges between components, instead we
  simply assume all remaining edges are negative after no more positive edges
  have been found after a period of time.

This new review scheme is a massive improvement of the existing review scheme.
However, it is sensitive to errors.
To accommodate this we augment the set of edges to review with a small random
  (or specially selected edges) set of redundant edges that could induce an
  inconsistent graph state and expose previously made errors.
We use a algorithm based on minimum s-t-cut to suggest edges to re-review in
  the event of an error case.


\paragraph{Threshold Based Automated Review Algorithm}

To improve on this review scheme even further we make use further use of our
  learned probabilities.
We accept a high and low threshold and mark any edge scoring above the
  threshold as a match and any edge bellow it as a not match.
Any inconsistent edges are flagged and the rest of the algorithm is the same
  as the full review algorithm.
In this was we avoid presenting the user with any matches that are obviously
  correct thus reducing the number of manual reviews needed.
As the classification algorithm improves the thresholds can be adjusted until
  ideally human input is no longer needed.


\paragraph{Multi-Cut Based Automated Review Algorithm}

One more tweak we can make to the algorithm it to use multicut instead of the
thresholding procedure.  The multicut algorithm chooses edges to group and then
those edges are marked as matches. To avoid errors we augment these results
with the threshold results in order to induce error states on components.


\paragraph{Active Learning}
Because training a random forest classifier is quick we use reviewed edges to augment 
our training data and periodically retrain the classifier in the background as
the user makes more reviews. Once the classifier is trained, the probabilities
on unreviewed edges are updated and inferred if they are above the threshold / part of the multicut.


\paragraph{Component Confidence}
One state we wish to avoid is when a group of annotations are marked as the
  same because they belong to a very long chain.
In practice the probability that the annotations on the endpoints of those
  chains are the same is actually quite low unless the reviewer is perfect.

Given a component of annotations we wish to compute the probability that each
  pair of annotation is the same.
In the case where there is a user review between then then that probability is
  a prior probability that the user makes accurate reviews (which is probably
  somewhere between $.8$ and $.95$).
If there is a one-vs-one edge then we can use that probability.
If there is not a one-vs-one edge (because that edge was not suggested by the
  one-vs-many results) then we need to find a good way to compute that
  probability.


As a baseline we implement a very simple algorithm.
We specific two thresholds:
a positive jump threshold and a negative jump threshold:
$t_{posjump}$  and $t_{negjump}$.
The positive jump threshold states that if an two nodes within a connected
  component are separated by more than $t_{posjump}$ positive review edges then
  any unreviewed edges that could decrease that distance are added back into the
  priority queue.
Likewise, the negative jump threshold states that nodes between negative
  components should not be separated by more than a $t_{negjump}$ distance over
  positive or negative reviewed edges.
In the automated case this heuristic can be augmented to consider edges above
  or below the scoring threshold as reviewed.


To improve this algorithm we have a few ideas that we suggest for future work:

Probability along shortest comparable positive path.

Probability based on posteriors of a 3-clique MRF inference.
I like this one best and the challenge here is to add edges the component to
  make it a clique, then add a probability between them (maybe compute it using
  the RF or use some prior).


  The factor graph looks like this for $P(e_{12} | e_{13}, e_{23})$.

\begin{verbatim}

    (1)
   /   \
  /     \
(2)-----(3)


e_{12}     | e_{13}    || e_{23}
==========================================================================
 match     |  match    || match=alpha, no-match=0.0,  not-comp=(1 - alpha)
 match     |  no-match || match=0.0,   no-match=beta, not-comp=(1 - beta)
 no-match  |  match    || match=0.0,   no-match=beta, not-comp=(1 - beta)
 no-match  |  no-match || match=1/3,   no-match=1/3,  not-comp=1/3
 -------------------------------------------------------------------------
 match     |  not-comp || match=1/3,   no-match=1/3,  not-comp=1/3
 no-match  |  not-comp || match=1/3,   no-match=1/3,  not-comp=1/3
 not-comp  |  match    || match=1/3,   no-match=1/3,  not-comp=1/3
 not-comp  |  no-match || match=1/3,   no-match=1/3,  not-comp=1/3
 not-comp  |  not-comp || match=1/3,   no-match=1/3,  not-comp=1/3


 where alpha and beta are prior parameters in the ranges
 1.0 > alpha > .5
 1.0 > beta > .5

 I'm thinking something like alpha=.8 and beta=.8

\end{verbatim}

The two main states that matter are:
(1) when two of the three edges match, in that case the third edge is very
likely to be a match, it might be not-comparable, but it is impossible for it
to be not a match.

(2) when one edge is a match another edges is a not match, then the last edge
is very likely not a match, it might be not-comparable, but it is impossible
for it to be a match.

All other states end up not giving any information about the state of the third
match.  Perhaps its not exactly a uniform distribution, but whatever it is, it
will be close.


Constructing this factor graph on all 3-cliques in a component will allow us to
run belief propagation to compute a posterior probability over each edge.
Edges with a low posterior probability can be flagged for further verification. 
Then that probability will be updated to the user probabilities and the
posterior can be recomputed until the entire component is above a threshold of
confidence (indicated by the max of the probabilities of no-match over all
  edges).



\section{Experiments and Results}

To demonstrate the results of enriching features with one-vs-one
  correspondences we perform the following experiment.
We select a set of annotation pairs using the method outlined earlier.
We first assign each pair a score using its baseline LNBNN score computed
  earlier.
If no score was computed it is given a score of zero.
We then apply one-vs-one matching augmentation to each pair and score each
  pair using the ratio test.
We then apply spatial verification on top of the one-vs-one augmentation.
The results of this test are as follows using the AUC of the ROC curve to
  indicate separability.
  
To further improve on these baseline results we apply a learning stage using a
random forest classifier. To avoid bias hyperparameter settings are fixed to
the optimal settings found using a grid search on an external dataset. 
We estimate performance of the learning algorithm using 10-fold cross
validation on the experimental dataset. The average over these runs is the
score we report.


\begin{verbatim}

Plains Zebras (PZ_Master1)
| Method          |    AUC | % error decrease |
|-----------------+--------+------------------|
| 1vM-LNBNN       | 0.9388 |              0.0 |
| 1v1-RAT         | 0.9499 |            18.09 |
| 1v1-RAT+SVER    | 0.9505 |            19.10 |
| 1v1-RAT+SVER+RF | 0.9738 |            57.28 |

Grevy's Zebras (GZ_Master1)
| Method          |    AUC | % error decrease |
|-----------------+--------+------------------|
| 1vM-LNBNN       | 0.9363 |             0.00 |
| 1v1-RAT         | 0.9646 |            44.42 |
| 1v1-RAT+SVER    | 0.9668 |            47.88 |
| 1v1-RAT+SVER+RF | 0.9810 |            70.17 |

\end{verbatim}


\paragraph{SMK Results}

\begin{verbatim}

Plains zebras: (PZ_Master1)
| Method     | % correct @ rank #1 |
|------------+---------------------|
| 1vM-LNBNN  | 75.60               |
| VLAD-ASMK  | 69.69               |

Grevy's zebras:  (GZ_Master1)
| Method     | % correct @ rank #1 |
|------------+---------------------|
| 1vM-LNBNN  | 84.94               |
| VLAD-ASMK  | 70.87               |

\end{verbatim}

These results are without spatial verification or foregroundness weighting.
The ASMK results are slightly above what they should be because I trained the
  vocabulary using the database annotations, which will cause some amount of
  overfitting.
This shows that the LNBNN algorithm still outperforms SMK even when SMK has a
  clear advantage.
We have have tested our SMK implementation by reproducing the results on
  standard datasets~\cite{tolias_2012} to ensure that it has the best chance
  possible to match the results of the LNBNN algorithm.
These results indicate that quantization error is still a problem when using 
a fixed length annotation wide image representation.
The fine detail captured by local descriptors is lost in the aggregation.


\paragraph{Variable Importance}

Our intuition is that matching is driven by a small subset of very distinctive
  features on these animals and not by the combined distinctivness over all
  features.

Interestingly we find that the most important features are aggregate
  statistics instead of the selected top matches.

Perhaps the top scoring matches do not reliably map to the distinctive
descriptors driving the matching. 

The weighted variable importance for Grevy's zebras is: 
\begin{verbatim}

Plains zebras: (PZ_Master1)
nonan
{
    'sum_norm_dist'      : 0.2121,
    'n_total'            : 0.1504,
    'sum_match_dist'     : 0.1479,
    'sum_lnbnn_norm_dist': 0.1249,
    'sum_ratio'          : 0.1197,
    'sum_sver_err_xy'    : 0.1104,
    'sum_sver_err_ori'   : 0.0557,
    'sum_sver_err_scale' : 0.0435,
    'yaw_delta'          : 0.0155,
    'sum_lnbnn'          : 0.0070,
    'yaw_1'              : 0.0067,
    'yaw_2'              : 0.0062,
}
withnan
{
    'sum_norm_dist'                   : 0.0642,
    'n_total'                         : 0.0617,
    'sum_match_dist'                  : 0.0543,
    'sum_ratio'                       : 0.0480,
    'sum_lnbnn_norm_dist'             : 0.0421,
    'mean_ratio'                      : 0.0417,
    'std_sver_err_xy'                 : 0.0351,
    'mean_sver_err_xy'                : 0.0333,
    'mean_lnbnn_norm_dist'            : 0.0298,
    'std_ratio'                       : 0.0259,
    'sum_sver_err_xy'                 : 0.0249,
    'mean_sver_err_ori'               : 0.0200,
    'lnbnn2_sver_err_ori'             : 0.0182,
    'std_sver_err_ori'                : 0.0175,
    'match_dist1_sver_err_ori'        : 0.0152,
    'std_norm_dist'                   : 0.0132,
    'norm_dist2_sver_err_ori'         : 0.0131,
    'std_lnbnn_norm_dist'             : 0.0129,
    'norm_dist1_sver_err_ori'         : 0.0123,
    'ratio2_sver_err_ori'             : 0.0123,
    'ratio2_ratio'                    : 0.0123,
    'lnbnn_norm_dist1_sver_err_ori'   : 0.0119,
    'mean_match_dist'                 : 0.0119,
    'lnbnn_norm_dist0_sver_err_ori'   : 0.0117,
    'sum_sver_err_ori'                : 0.0106,
    'match_dist0_sver_err_ori'        : 0.0096,
    'time_delta'                      : 0.0094,
    'std_match_dist'                  : 0.0093,
    'match_dist2_sver_err_ori'        : 0.0089,
    'ratio1_ratio'                    : 0.0078,
    'gps_delta'                       : 0.0078,
    'std_sver_err_scale'              : 0.0078,
    'time_1'                          : 0.0075,
    'norm_dist0_sver_err_ori'         : 0.0071,
    'time_2'                          : 0.0067,
    'lnbnn_norm_dist2_sver_err_ori'   : 0.0066,
    'lnbnn1_sver_err_ori'             : 0.0065,
    'lnbnn2_sver_err_xy'              : 0.0061,
    'ratio1_sver_err_ori'             : 0.0057,
    'ratio2_sver_err_xy'              : 0.0056,
    'ratio2_sver_err_scale'           : 0.0056,
    'match_dist1_sver_err_scale'      : 0.0055,
    'match_dist2_sver_err_scale'      : 0.0054,
    'lnbnn0_sver_err_ori'             : 0.0050,
    'ratio0_sver_err_ori'             : 0.0049,
    'norm_dist2_sver_err_scale'       : 0.0049,
    'sum_sver_err_scale'              : 0.0048,
    'lnbnn_norm_dist2_sver_err_xy'    : 0.0045,
    'norm_dist2_sver_err_xy'          : 0.0044,
    'gps0_2'                          : 0.0043,
    'speed'                           : 0.0040,
    'gps0_1'                          : 0.0040,
    'lnbnn1_sver_err_scale'           : 0.0040,
    'yaw_delta'                       : 0.0039,
    'gps1_1'                          : 0.0038,
    'gps1_2'                          : 0.0038,
    'norm_dist1_sver_err_xy'          : 0.0036,
    'lnbnn0_sver_err_xy'              : 0.0036,
    'match_dist2_sver_err_xy'         : 0.0036,
    'lnbnn1_sver_err_xy'              : 0.0036,
    'lnbnn_norm_dist2_lnbnn_norm_dist': 0.0034,
    'ratio1_sver_err_scale'           : 0.0033,
    'ratio0_sver_err_scale'           : 0.0033,
    'match_dist0_sver_err_xy'         : 0.0030,
    'match_dist1_sver_err_xy'         : 0.0029,
    'lnbnn_norm_dist1_sver_err_xy'    : 0.0029,
    'ratio0_sver_err_xy'              : 0.0029,
    'lnbnn0_sver_err_scale'           : 0.0027,
    'mean_norm_dist'                  : 0.0027,
    'lnbnn_norm_dist0_sver_err_xy'    : 0.0027,
    'norm_dist0_sver_err_xy'          : 0.0026,
    'lnbnn_norm_dist2_sver_err_scale' : 0.0026,
    'lnbnn_norm_dist1_sver_err_scale' : 0.0026,
    'lnbnn2_lnbnn_norm_dist'          : 0.0026,
    'qual_2'                          : 0.0025,
    'qual_1'                          : 0.0025,
    'ratio1_sver_err_xy'              : 0.0025,
    'norm_dist2_lnbnn_norm_dist'      : 0.0025,
    'norm_dist2_match_dist'           : 0.0022,
    'match_dist1_lnbnn_norm_dist'     : 0.0022,
    'norm_dist2_ratio'                : 0.0022,
    'lnbnn_norm_dist2_norm_dist'      : 0.0021,
    'lnbnn0_lnbnn_norm_dist'          : 0.0021,
    'mean_sver_err_scale'             : 0.0021,
    'norm_dist1_lnbnn_norm_dist'      : 0.0020,
    'match_dist0_lnbnn_norm_dist'     : 0.0020,
    'norm_dist0_sver_err_scale'       : 0.0020,
    'match_dist2_norm_dist'           : 0.0020,
    'match_dist2_lnbnn_norm_dist'     : 0.0020,
    'lnbnn1_lnbnn_norm_dist'          : 0.0020,
    'ratio2_norm_dist'                : 0.0019,
    'lnbnn_norm_dist1_lnbnn_norm_dist': 0.0019,
    'norm_dist0_lnbnn_norm_dist'      : 0.0019,
    'norm_dist1_sver_err_scale'       : 0.0019,
    'match_dist0_sver_err_scale'      : 0.0019,
    'lnbnn_norm_dist0_lnbnn_norm_dist': 0.0019,
    'ratio2_lnbnn_norm_dist'          : 0.0017,
    'ratio0_ratio'                    : 0.0017,
    'ratio0_lnbnn_norm_dist'          : 0.0015,
    'ratio1_lnbnn_norm_dist'          : 0.0014,
    'lnbnn_norm_dist0_ratio'          : 0.0014,
    'match_dist0_ratio'               : 0.0014,
    'lnbnn_norm_dist2_match_dist'     : 0.0014,
    'norm_dist1_ratio'                : 0.0014,
    'lnbnn0_match_dist'               : 0.0013,
    'lnbnn2_ratio'                    : 0.0013,
    'norm_dist1_norm_dist'            : 0.0013,
    'norm_dist0_ratio'                : 0.0013,
    'norm_dist2_norm_dist'            : 0.0013,
    'lnbnn_norm_dist1_match_dist'     : 0.0013,
    'lnbnn0_norm_dist'                : 0.0013,
    'qual_delta'                      : 0.0013,
    'lnbnn_norm_dist2_ratio'          : 0.0013,
    'lnbnn1_ratio'                    : 0.0013,
    'match_dist1_ratio'               : 0.0013,
    'lnbnn_norm_dist1_ratio'          : 0.0013,
    'norm_dist1_match_dist'           : 0.0013,
    'match_dist2_match_dist'          : 0.0013,
    'lnbnn2_norm_dist'                : 0.0013,
    'lnbnn_norm_dist1_norm_dist'      : 0.0013,
    'lnbnn_norm_dist0_norm_dist'      : 0.0013,
    'match_dist1_norm_dist'           : 0.0012,
    'match_dist0_norm_dist'           : 0.0012,
    'lnbnn0_ratio'                    : 0.0012,
    'ratio1_norm_dist'                : 0.0012,
    'lnbnn1_match_dist'               : 0.0012,
    'lnbnn2_match_dist'               : 0.0012,
    'lnbnn_norm_dist0_match_dist'     : 0.0012,
    'norm_dist0_match_dist'           : 0.0012,
    'match_dist1_match_dist'          : 0.0012,
    'ratio2_match_dist'               : 0.0012,
    'match_dist2_ratio'               : 0.0012,
    'lnbnn_norm_dist0_sver_err_scale' : 0.0012,
    'norm_dist0_norm_dist'            : 0.0012,
    'match_dist0_match_dist'          : 0.0012,
    'ratio1_match_dist'               : 0.0012,
    'lnbnn1_norm_dist'                : 0.0011,
    'ratio0_match_dist'               : 0.0011,
    'lnbnn2_sver_err_scale'           : 0.0011,
    'ratio0_norm_dist'                : 0.0011,
    'yaw_1'                           : 0.0011,
    'yaw_2'                           : 0.0010,
    'sum_lnbnn'                       : 0.0005,
    'mean_lnbnn'                      : 0.0004,
    'std_lnbnn'                       : 0.0004,
    'lnbnn1_lnbnn'                    : 0.0000,
    'lnbnn_norm_dist0_lnbnn'          : 0.0000,
    'lnbnn0_lnbnn'                    : 0.0000,
    'lnbnn_norm_dist2_lnbnn'          : 0.0000,
    'lnbnn2_lnbnn'                    : 0.0000,
    'lnbnn_norm_dist1_lnbnn'          : 0.0000,
    'match_dist0_lnbnn'               : 0.0000,
    'norm_dist1_lnbnn'                : 0.0000,
    'match_dist2_lnbnn'               : 0.0000,
    'norm_dist2_lnbnn'                : 0.0000,
    'match_dist1_lnbnn'               : 0.0000,
    'norm_dist0_lnbnn'                : 0.0000,
    'ratio0_lnbnn'                    : 0.0000,
    'ratio1_lnbnn'                    : 0.0000,
    'ratio2_lnbnn'                    : 0.0000,
}
withnan_ratio
{
    'sum_norm_dist'        : 0.1053,
    'sum_match_dist'       : 0.0862,
    'n_total'              : 0.0833,
    'sum_ratio'            : 0.0726,
    'mean_ratio'           : 0.0648,
    'std_sver_err_xy'      : 0.0485,
    'std_ratio'            : 0.0475,
    'mean_sver_err_xy'     : 0.0457,
    'sum_sver_err_xy'      : 0.0407,
    'mean_sver_err_ori'    : 0.0343,
    'std_norm_dist'        : 0.0255,
    'mean_match_dist'      : 0.0218,
    'std_sver_err_ori'     : 0.0185,
    'ratio2_ratio'         : 0.0183,
    'std_match_dist'       : 0.0168,
    'sum_sver_err_ori'     : 0.0164,
    'ratio2_sver_err_ori'  : 0.0153,
    'time_delta'           : 0.0151,
    'gps_delta'            : 0.0127,
    'std_sver_err_scale'   : 0.0122,
    'ratio2_sver_err_xy'   : 0.0120,
    'time_1'               : 0.0114,
    'ratio2_sver_err_scale': 0.0109,
    'ratio1_sver_err_ori'  : 0.0109,
    'ratio0_sver_err_ori'  : 0.0104,
    'time_2'               : 0.0100,
    'ratio1_ratio'         : 0.0096,
    'speed'                : 0.0071,
    'ratio0_sver_err_xy'   : 0.0071,
    'mean_norm_dist'       : 0.0069,
    'gps0_2'               : 0.0067,
    'sum_sver_err_scale'   : 0.0064,
    'ratio2_norm_dist'     : 0.0063,
    'ratio1_sver_err_scale': 0.0062,
    'gps1_2'               : 0.0061,
    'gps0_1'               : 0.0061,
    'yaw_delta'            : 0.0060,
    'gps1_1'               : 0.0059,
    'ratio1_sver_err_xy'   : 0.0057,
    'mean_sver_err_scale'  : 0.0055,
    'ratio0_ratio'         : 0.0054,
    'ratio0_sver_err_scale': 0.0050,
    'ratio2_match_dist'    : 0.0048,
    'qual_2'               : 0.0044,
    'qual_1'               : 0.0041,
    'ratio1_norm_dist'     : 0.0034,
    'ratio1_match_dist'    : 0.0033,
    'ratio0_match_dist'    : 0.0030,
    'ratio0_norm_dist'     : 0.0029,
    'qual_delta'           : 0.0021,
    'yaw_1'                : 0.0017,
    'yaw_2'                : 0.0015,
}




Grevy's Zebras (GZ_Master1)
For the classifier trained without any nan-values
nonan
{
    'n_total'            : 0.2718,
    'sum_norm_dist'      : 0.1956,
    'sum_ratio'          : 0.1679,
    'sum_match_dist'     : 0.1017,
    'sum_sver_err_xy'    : 0.0973,
    'sum_lnbnn_norm_dist': 0.0830,
    'sum_sver_err_ori'   : 0.0452,
    'sum_sver_err_scale' : 0.0320,
    'sum_lnbnn'          : 0.0056,
}
withnan
{
    'sum_norm_dist'                   : 0.0917,
    'n_total'                         : 0.0790,
    'sum_match_dist'                  : 0.0634,
    'sum_lnbnn_norm_dist'             : 0.0559,
    'sum_ratio'                       : 0.0559,
    'mean_ratio'                      : 0.0526,
    'mean_match_dist'                 : 0.0501,
    'mean_sver_err_ori'               : 0.0307,
    'sum_sver_err_ori'                : 0.0298,
    'std_ratio'                       : 0.0293,
    'mean_sver_err_xy'                : 0.0266,
    'std_sver_err_ori'                : 0.0199,
    'norm_dist2_sver_err_ori'         : 0.0123,
    'lnbnn1_sver_err_ori'             : 0.0122,
    'mean_norm_dist'                  : 0.0119,
    'match_dist2_sver_err_ori'        : 0.0114,
    'norm_dist1_sver_err_ori'         : 0.0113,
    'time_delta'                      : 0.0112,
    'lnbnn_norm_dist1_sver_err_ori'   : 0.0109,
    'std_sver_err_xy'                 : 0.0104,
    'sum_sver_err_scale'              : 0.0089,
    'lnbnn_norm_dist2_sver_err_ori'   : 0.0085,
    'speed'                           : 0.0084,
    'lnbnn_norm_dist0_sver_err_ori'   : 0.0084,
    'gps_delta'                       : 0.0076,
    'std_match_dist'                  : 0.0073,
    'match_dist1_sver_err_ori'        : 0.0072,
    'norm_dist1_sver_err_xy'          : 0.0066,
    'std_norm_dist'                   : 0.0066,
    'mean_lnbnn_norm_dist'            : 0.0063,
    'norm_dist0_sver_err_ori'         : 0.0062,
    'ratio2_sver_err_ori'             : 0.0062,
    'norm_dist2_sver_err_xy'          : 0.0061,
    'lnbnn_norm_dist2_sver_err_xy'    : 0.0059,
    'sum_sver_err_xy'                 : 0.0058,
    'match_dist2_sver_err_xy'         : 0.0056,
    'lnbnn2_sver_err_xy'              : 0.0055,
    'lnbnn2_sver_err_ori'             : 0.0054,
    'match_dist0_sver_err_ori'        : 0.0053,
    'ratio1_sver_err_ori'             : 0.0053,
    'lnbnn_norm_dist0_sver_err_xy'    : 0.0048,
    'match_dist0_sver_err_xy'         : 0.0047,
    'match_dist1_sver_err_xy'         : 0.0046,
    'ratio2_sver_err_xy'              : 0.0042,
    'norm_dist0_sver_err_xy'          : 0.0042,
    'lnbnn_norm_dist1_sver_err_scale' : 0.0038,
    'time_1'                          : 0.0038,
    'lnbnn1_sver_err_xy'              : 0.0037,
    'ratio0_sver_err_ori'             : 0.0036,
    'lnbnn_norm_dist1_sver_err_xy'    : 0.0035,
    'norm_dist1_sver_err_scale'       : 0.0034,
    'std_lnbnn_norm_dist'             : 0.0033,
    'time_2'                          : 0.0032,
    'ratio2_ratio'                    : 0.0032,
    'ratio0_sver_err_xy'              : 0.0032,
    'gps1_1'                          : 0.0032,
    'match_dist2_sver_err_scale'      : 0.0031,
    'ratio1_sver_err_xy'              : 0.0030,
    'gps0_1'                          : 0.0029,
    'gps1_2'                          : 0.0028,
    'lnbnn_norm_dist2_norm_dist'      : 0.0027,
    'gps0_2'                          : 0.0026,
    'lnbnn_norm_dist2_match_dist'     : 0.0025,
    'lnbnn0_sver_err_ori'             : 0.0024,
    'lnbnn2_sver_err_scale'           : 0.0024,
    'lnbnn_norm_dist0_sver_err_scale' : 0.0024,
    'mean_sver_err_scale'             : 0.0023,
    'lnbnn_norm_dist2_sver_err_scale' : 0.0023,
    'std_sver_err_scale'              : 0.0022,
    'lnbnn2_lnbnn_norm_dist'          : 0.0020,
    'norm_dist2_sver_err_scale'       : 0.0020,
    'match_dist2_ratio'               : 0.0019,
    'ratio2_sver_err_scale'           : 0.0019,
    'match_dist2_lnbnn_norm_dist'     : 0.0019,
    'lnbnn_norm_dist2_ratio'          : 0.0018,
    'ratio2_match_dist'               : 0.0018,
    'lnbnn2_norm_dist'                : 0.0018,
    'ratio1_sver_err_scale'           : 0.0017,
    'match_dist1_sver_err_scale'      : 0.0017,
    'match_dist1_match_dist'          : 0.0017,
    'ratio1_ratio'                    : 0.0017,
    'norm_dist0_lnbnn_norm_dist'      : 0.0017,
    'lnbnn0_lnbnn_norm_dist'          : 0.0016,
    'lnbnn1_lnbnn_norm_dist'          : 0.0016,
    'match_dist2_match_dist'          : 0.0016,
    'lnbnn0_sver_err_xy'              : 0.0016,
    'match_dist0_sver_err_scale'      : 0.0016,
    'lnbnn1_sver_err_scale'           : 0.0016,
    'match_dist0_lnbnn_norm_dist'     : 0.0015,
    'norm_dist1_match_dist'           : 0.0015,
    'ratio2_norm_dist'                : 0.0015,
    'lnbnn1_match_dist'               : 0.0015,
    'yaw_1'                           : 0.0015,
    'lnbnn2_match_dist'               : 0.0015,
    'lnbnn2_ratio'                    : 0.0015,
    'match_dist1_lnbnn_norm_dist'     : 0.0015,
    'lnbnn_norm_dist1_ratio'          : 0.0015,
    'lnbnn_norm_dist0_lnbnn_norm_dist': 0.0014,
    'ratio2_lnbnn_norm_dist'          : 0.0014,
    'norm_dist0_sver_err_scale'       : 0.0014,
    'lnbnn_norm_dist2_lnbnn_norm_dist': 0.0014,
    'lnbnn_norm_dist0_ratio'          : 0.0014,
    'lnbnn1_ratio'                    : 0.0014,
    'norm_dist2_lnbnn_norm_dist'      : 0.0014,
    'norm_dist1_lnbnn_norm_dist'      : 0.0013,
    'ratio0_sver_err_scale'           : 0.0013,
    'match_dist1_ratio'               : 0.0013,
    'lnbnn_norm_dist1_lnbnn_norm_dist': 0.0013,
    'yaw_delta'                       : 0.0012,
    'norm_dist0_ratio'                : 0.0012,
    'ratio0_lnbnn_norm_dist'          : 0.0012,
    'norm_dist2_match_dist'           : 0.0012,
    'lnbnn_norm_dist1_match_dist'     : 0.0012,
    'norm_dist2_ratio'                : 0.0012,
    'lnbnn0_norm_dist'                : 0.0012,
    'match_dist0_match_dist'          : 0.0011,
    'lnbnn0_sver_err_scale'           : 0.0011,
    'match_dist0_ratio'               : 0.0011,
    'lnbnn_norm_dist0_match_dist'     : 0.0011,
    'norm_dist0_match_dist'           : 0.0011,
    'norm_dist1_ratio'                : 0.0011,
    'lnbnn0_match_dist'               : 0.0011,
    'lnbnn0_ratio'                    : 0.0010,
    'ratio0_match_dist'               : 0.0010,
    'ratio1_match_dist'               : 0.0010,
    'lnbnn1_norm_dist'                : 0.0010,
    'norm_dist1_norm_dist'            : 0.0010,
    'ratio0_ratio'                    : 0.0009,
    'norm_dist0_norm_dist'            : 0.0009,
    'ratio1_lnbnn_norm_dist'          : 0.0009,
    'lnbnn_norm_dist1_norm_dist'      : 0.0009,
    'match_dist0_norm_dist'           : 0.0009,
    'match_dist1_norm_dist'           : 0.0009,
    'ratio1_norm_dist'                : 0.0009,
    'norm_dist2_norm_dist'            : 0.0009,
    'match_dist2_norm_dist'           : 0.0009,
    'ratio0_norm_dist'                : 0.0009,
    'lnbnn_norm_dist0_norm_dist'      : 0.0008,
    'yaw_2'                           : 0.0008,
    'qual_1'                          : 0.0008,
    'qual_2'                          : 0.0006,
    'mean_lnbnn'                      : 0.0004,
    'qual_delta'                      : 0.0004,
    'std_lnbnn'                       : 0.0004,
    'sum_lnbnn'                       : 0.0002,
    'lnbnn_norm_dist2_lnbnn'          : 0.0001,
    'lnbnn0_lnbnn'                    : 0.0000,
    'match_dist0_lnbnn'               : 0.0000,
    'norm_dist1_lnbnn'                : 0.0000,
    'lnbnn2_lnbnn'                    : 0.0000,
    'lnbnn1_lnbnn'                    : 0.0000,
    'norm_dist0_lnbnn'                : 0.0000,
    'match_dist2_lnbnn'               : 0.0000,
    'norm_dist2_lnbnn'                : 0.0000,
    'lnbnn_norm_dist0_lnbnn'          : 0.0000,
    'ratio0_lnbnn'                    : 0.0000,
    'lnbnn_norm_dist1_lnbnn'          : 0.0000,
    'ratio2_lnbnn'                    : 0.0000,
    'match_dist1_lnbnn'               : 0.0000,
    'ratio1_lnbnn'                    : 0.0000,
}
withnan_ratio
{
    'n_total'              : 0.1180,
    'sum_norm_dist'        : 0.1075,
    'sum_ratio'            : 0.0978,
    'sum_match_dist'       : 0.0811,
    'mean_ratio'           : 0.0763,
    'mean_match_dist'      : 0.0583,
    'mean_sver_err_ori'    : 0.0410,
    'mean_sver_err_xy'     : 0.0406,
    'sum_sver_err_ori'     : 0.0389,
    'std_ratio'            : 0.0382,
    'std_sver_err_ori'     : 0.0257,
    'std_sver_err_xy'      : 0.0184,
    'time_delta'           : 0.0181,
    'mean_norm_dist'       : 0.0163,
    'std_norm_dist'        : 0.0141,
    'sum_sver_err_xy'      : 0.0124,
    'speed'                : 0.0121,
    'gps_delta'            : 0.0117,
    'ratio2_sver_err_ori'  : 0.0114,
    'sum_sver_err_scale'   : 0.0112,
    'ratio2_sver_err_xy'   : 0.0103,
    'std_match_dist'       : 0.0102,
    'ratio1_sver_err_ori'  : 0.0099,
    'ratio0_sver_err_xy'   : 0.0086,
    'ratio1_sver_err_xy'   : 0.0086,
    'ratio0_sver_err_ori'  : 0.0081,
    'ratio2_sver_err_scale': 0.0068,
    'ratio2_ratio'         : 0.0066,
    'time_1'               : 0.0060,
    'std_sver_err_scale'   : 0.0058,
    'mean_sver_err_scale'  : 0.0056,
    'time_2'               : 0.0054,
    'ratio0_sver_err_scale': 0.0053,
    'gps1_1'               : 0.0049,
    'ratio1_sver_err_scale': 0.0047,
    'gps1_2'               : 0.0046,
    'gps0_1'               : 0.0044,
    'ratio1_ratio'         : 0.0043,
    'gps0_2'               : 0.0042,
    'ratio2_match_dist'    : 0.0034,
    'ratio1_norm_dist'     : 0.0031,
    'ratio2_norm_dist'     : 0.0027,
    'ratio1_match_dist'    : 0.0026,
    'ratio0_ratio'         : 0.0025,
    'ratio0_norm_dist'     : 0.0024,
    'ratio0_match_dist'    : 0.0024,
    'yaw_1'                : 0.0023,
    'yaw_delta'            : 0.0018,
    'qual_1'               : 0.0010,
    'yaw_2'                : 0.0010,
    'qual_2'               : 0.0007,
    'qual_delta'           : 0.0005,
}





\end{verbatim}
